Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-16 paper/paper.tex
wordings
nudge Fig 4

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}
%\usetikzlibrary{decorations}
%\usetikzlibrary{decorations.pathmorphing}

@@

The second approach is illustrated in Figure~\ref{fig:CEGIS} and uses a
two-stage verification: the first stage performs potentially unsound
fixed-point operations assuming a plant precision \param{I_p}{F_p}, and the
second stage restores soundness by validating these operations
using interval arithmetic on the synthesized controller.
%
\begin{figure*}[htb]
\centering
\resizebox{.8\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=7cm,
	minimum height=.8cm,
	label={\sc Verify},] (verif) {};
   \node[fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc ~Uncertainty~~~~}};
   \node[fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc ~~~~~Precision~~~}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \node (gp) {Closed-loop System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2cm]aux.center) {BMC-based Verifier};
   \node (fp)  at ([xshift=2cm]aux.center) {Fixed-point \\Arithmetic Verifier};
   }   
    \\
  };

@@

A third set of benchmarks uses a physical plant for satellite
applications~\cite{Franklin15}.  Satellites often require attitude (pose)
control for proper orientation of antennas and sensors w.r.t.~earth.  The
satellite attitude control is typically used for three-axis attitude
tracking, but here we consider only one axis at a time.  The motion equation
for the one-axis system, disregarding disturbance torques, is given by
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C}, 
\end{equation}
%
\noindent where $I$ is the inertia moment of the satellite about its mass
center, $\tau_{C}$ is the control torque applied by the thrusters, and
$\theta$ is the controlled attitude angle.  Normalizing
Eq.~\eqref{eq:satelliteode} by defining the control signal
$u=\frac{\tau_{C}}{I}$ and taking the Laplace transform, the following
$s$-domain transfer function $G(s)$ is obtained:
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}
%
\noindent Using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
we get the following $z$-domain model:
%
\begin{equation}
G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
\end{equation}

>>>>

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}
\usepackage[scaled]{helvet}

%\usetikzlibrary{decorations}
%\usetikzlibrary{decorations.pathmorphing}

@@

The second approach is illustrated in Figure~\ref{fig:CEGIS} and uses a
two-stage verification: the first stage performs potentially unsound
fixed-point operations assuming a plant precision \param{I_p}{F_p}, and the
second stage restores soundness by validating these operations
using interval arithmetic on the synthesized controller.
%
\begin{figure*}[htb]
\centering
\resizebox{.9\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=7cm,
	minimum height=1cm,
	label={\sc Verify},] (verif) {};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \node (gp) {\sf Closed-loop System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
   \node (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point \\\sf Arithmetic Verifier};
   }   
    \\
  };

@@

A third set of benchmarks uses a physical plant for satellite
applications~\cite{Franklin15}.  Satellites require attitude (pose) control
for orientation of antennas and sensors w.r.t.~earth.  The satellite
attitude control is typically used for three-axis attitude tracking, but
here we consider only one axis at a time.  The motion equation for the
one-axis system, disregarding disturbance torques, is given by
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C}, 
\end{equation}
%
\noindent where $I$ is the inertia moment of the satellite about its mass
center, $\tau_{C}$ is the control torque applied by the thrusters, and
$\theta$ is the controlled attitude angle.  Normalizing
Eq.~\eqref{eq:satelliteode} by defining the control signal
$u=\frac{\tau_{C}}{I}$ and taking the Laplace transform, the following
$s$-domain transfer function $G(s)$ is obtained:
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}
%
\noindent Using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
we get the following $z$-domain model:
%
\begin{equation}
G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
\end{equation}
